Water resource utilization regimes at a basin scale: transition framework and development traps

### 2020-08-23 tex/main/manuscript.tex
讨论第二节第三段

\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/traps.jpg}
	\caption{
		\textbf{Transition phases of water resources utilization regime and development traps.}
		Green arrows indicate the trajectory without falling into any development trap, IWRU roughly follows a non-linear upward trend at the same time. However, overexploitation of water resources will leave the system in a local resource trap, without moving to regional coordinated cycle. And even if one enters a regional cycle, it can still fall into a structural trap when water utilization fails to adapt to the complex changes within human-water systems.
	}
	\label{fig:traps}
\end{figure}

% 世界各大流域面临的问题。资源开发早期容易陷入资源陷阱；流域发展后期容易陷入结构陷阱。
According to case studies around the world, big river basins often face resource traps at the beginning of their developments, while highly developed ones often face structural traps.
% 黄河流域的发展过程，资源开发P2阶段陷入了资源陷阱（表现形式 xxx）。
During P1 and P2 (refers from natural cycle to the local cycle) in the Yellow River Basin, after the successive exploitation of agriculture, industry and services, the Water resource extraction rate has reached $79\%$, far exceeding the internationally recognized warning threshold of $40\%$. Although water management practices in P1 (construction of numerous reservoirs) mitigated the stress on water resources from accelerated development, it became scarce rapidly throughout and water utilization stresses rebounded in the P2 along with a regime shift. The resource trap is revealed at this point, with severe runoff outages and groundwater depletion of the Yellow River from P2 onwards (supplementary Fig. S8).
% 资源困局可能普遍存在
Since similar phenomena occurred in Mississippi and Indus River Basins, the fact that the accelerated development has been followed by water scarcity and a series of ecological problems shows that the resource traps is pervasive in the transition trajectory, especially from natural cycle to local cycle 
\cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011}.

% 后来摆脱了资源陷阱（表现形式 xxx）。
Faced with a clear resource trap, a clear transformation path towards integrated basin management was proposed
that has contributed to the gradual escape of the Yellow River from the resource trap.
.....
In short, these integrated management practices made the utilization of water resources into a regime of unified scheduling, 
in the Yellow River Basin 
to escape from the “resource trap” of economic expansion and accelerated resource depletion.
Similarly, 
many of the world's major river basins have eventually moved towards a system of integrated management and integrated dispatch, 
especially the XXX and XXX basins, 
where water resources are extremely scarce.

% 展望：未来还可能陷入结构陷阱，（表现形式：用水效率悖论的同时，灵活性进一步降低，
However, Despite achieving integrated management and escaping through increased water efficiency, 
basins still face new structural traps and require further transformation.
Firstly, in line with paradox of irrigation efficiency \cite{graftonParadoxIrrigationEfficiency2018}, 
significant improvement in agricultural irrigation efficiency (or decline in water use intensity) 
has been accompanied by a resurgence in irrigated area, 
resulting in an unabated and weak upward trend in water stress.
% 水资源压力仍在增大，而节水能力已经进入瓶颈，倾向性贡献减少）
As integrated basin allocation dominates water allocation, 
the propensity to allocate water between non-supply industries, such as industrial services, 
and agriculture is becoming fixed.
At the same time, the flexibility of water use is declining since domestic water use and thermal water use growth rapidly. 
Typically, similar to other cases, these may lead to a reduction in watershed resilience 
and leave highly coupled human-water systems facing greater vulnerability to collapse 
-- a typically structural trap.
% 下一步：可以通过统一调控，调整格局来调整结构，突破结构陷阱。
% 总结：整个流域需进一步转型与适应，以实现高质量发展。
Therefore, based on the identification of the current basin transition stage and development dilemma, 
further transitional governance is still needed to achieve high-quality sustainable development of the basin.

>>>>

\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/traps.jpg}
	\caption{
		\textbf{Transition phases of water resources utilization regime and development traps.}
		Green arrows indicate the trajectory without falling into any development trap, IWRU roughly follows a non-linear upward trend at the same time. However, overexploitation of water resources will leave the system in a resource trap, without moving to regional coordinated cycle. And even if one enters a regional cycle, it can still fall into a structural trap when water utilization fails to adapt to the complex changes within human-water systems.
	}
	\label{fig:traps}
\end{figure}

% 世界各大流域面临的问题。资源开发早期容易陷入资源陷阱；流域发展后期容易陷入结构陷阱。
According to case studies around the world, big river basins often face resource traps at the beginning of their developments, while highly developed ones often face structural traps.
% 黄河流域的发展过程，资源开发P2阶段陷入了资源陷阱（表现形式 xxx）。
During P1 and P2 (refers from natural cycle to the regional cycle) in the Yellow River Basin, after the successive exploitation of agriculture, industry and services, the Water resource extraction rate has reached $79\%$, far exceeding the internationally recognized warning threshold of $40\%$. Although water management practices in P1 (construction of numerous reservoirs) mitigated the stress on water resources from accelerated development, it became scarce rapidly throughout and water utilization stresses rebounded in the P2 along with a regime shift. The resource trap is revealed at this point, with severe runoff outages and groundwater depletion of the Yellow River from P2 onwards (supplementary Fig. S8).
% 资源困局可能普遍存在
Since similar phenomena occurred in Mississippi and Indus River Basins, the fact that the accelerated development has been followed by water scarcity and a series of ecological problems shows that the resource traps is pervasive in the transition trajectory, especially from natural cycle to regional cycle 
\cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011}.

% 后来摆脱了资源陷阱（表现形式 xxx）。
To get rid of the resource trap, a clear transformation towards integrated basin management was proposed, with several management practices (supplementary Methods S4 and Fig. S9). The most important of these is the “87 Water Allocation Scheme”, which adopts a top-down approach in allocating water resources to all regions and sectors \cite{wangThirtyYearsYellow2018}. Since then, the scheme has been revised and refined, and a comprehensive water resources utilization system has gradually been formed that takes the basin scale into account \cite{wangThirtyYearsYellow2018}. These integrated management practices made the utilization of water resources into a regime of unified scheduling since the P3 in the Yellow River Basin, to escape from the “resource trap”. Similarly, many of the world's major river basins have eventually moved towards a system of integrated governance, especially for trans-boundary rivers (e.g. Danube and Mekong River), where water resources are in need of collaborative governance \cite{bodinCollaborativeEnvironmentalGovernance2017a}.

% 展望：未来还可能陷入结构陷阱，（表现形式：用水效率悖论的同时，灵活性进一步降低，
However, in the regional cycle regime of water utilization, basins still face new structural traps and require further transformation. Firstly, in line with paradox of irrigation efficiency \cite{graftonParadoxIrrigationEfficiency2018}, significant improvement in agricultural irrigation efficiency (or decline in water use intensity) has been accompanied by a resurgence in irrigated area, 
resulting in an unabated and weak upward trend in water stress.
% 水资源压力仍在增大，而节水能力已经进入瓶颈，倾向性贡献减少）
As integrated basin allocation dominates water allocation, the propensity to allocate water between non-supply industries, such as industrial services, and agriculture is becoming fixed. At the same time, the flexibility of water use is declining since domestic water use and thermal water use growth rapidly. Typically, similar to other cases, these may lead to a reduction in watershed resilience and leave highly coupled human-water systems facing greater vulnerability to collapse --a typically structural trap.
% 下一步：可以通过统一调控，调整格局来调整结构，突破结构陷阱。
% 总结：整个流域需进一步转型与适应，以实现高质量发展。
Therefore, based on the identification of the current basin transition stage and development dilemma, 
further transitional governance is still needed to achieve high-quality sustainable development of the basin.
